Transforming Trash as an Artistic Act

### 2016-01-08 chapter1_reduced.tex
Committee Copy
Former-commit-id: 4798a7cb56c31623135a8d42eb713cb8e932ebe7
thesis format.
Former-commit-id: dc2842cb1dd0002e86ccf734ecdb5b11009dd346
updates
Former-commit-id: ed8c3a549dfd42e9a1714a8835097ccd033fd632
reorganization
Former-commit-id: e5cf9d1ed889ae9676d7eb070201bb31780d7a02

%
% FROM Trash as Treasure BY WILLIAM L. FASH AND E. WYLLYS ANDREWS, ReVista
%\summary{Facts}
\begin{singlespace}
\begin{quote}
The World Bank estimates that the amount of solid waste generated in cities is growing faster than the rate of urbanization. The higher the income level and the rate of urbanization, the greater the amount of solid waste produced. OECD\footnote{OECD (Organization for Economic Co-operation and Development) is an international economic organization of 34 countries. Turkey is a member of this organization.} countries produce almost half of the world’s waste. Africa and South Asia produce the least waste. High-income countries have the highest collection rates and are most likely to dispose of waste to landfills or incinerators. Low-income countries have the lowest collection rates and are most likely to dispose of their waste in open dumps. However, low-income countries also have the largest numbers of informal waste pickers who collect, sort, and reclaim recyclables---thus reducing costs to the city and to the environment \citep{fash2015trash}.
\end{quote}
\end{singlespace}

@@

%
%
%\summary{Parts of us}
\begin{singlespace}
\begin{quote}
Our trash is a testament; what we throw away says much about our values, our habits, and our lives. ... Our trash is part of us, whether or not we choose to acknowledge it. ... The absence of a waste stream aroused suspicion, just as the presence of particular items tell us about the habits of the consumers who generate a waste stream. \citep{zimring2012encyclopedia}
\end{quote}
\end{singlespace}

@@

%
%
%\summary{Different disciplines of trash, narrowing down scope}
Trash attract the attention of different peoples and disciplines \quotes{ranging from economics to environmental studies, but most particularly by those studying consumerism or material culture} \citep{emgin2012trashion}.

Technological perspectives are one them. Trash is seen as a design and technological problem \citep{mcdonough2010cradle}.  
% Developed technologies and societies generates lots of trash, so this situation cause to inquiry that are they really developed? Developed in what sense? What are the criterion (foundation, measure) of technology? Technology is interested in which problems?)

@@

% FROM Recycled, Re-Seen: Folk Art from the Global Scrap Heap
In addition to these
\begin{singlespace}
\begin{quote} 
the process of [transformation] is not to be confused with the kind of industrial recycling to which we in the West are most accustomed. When we think of recycling in industrialized nations we imagine an automated sequence beginning with the curbside disposal of aluminum cans, plastic bottles, and old newspapers with the aim of returning them to the industrial process \citep{cerny1996recycled}. 
\end{quote}
\end{singlespace}

@@

% FROM Rubbish! The Archaeology of Garbage, p.9, rathje1992rubbish
\begin{singlespace}
\begin{quote}
Several words for the things we throw away---"garbage", "trash", "refuse", "rubbish"--- are used synonymously in causal speech but in fact have different meanings. \textit{Trash} refers specifically to discards that are at least theoretically "dry"---newspapers, boxes, cans, and so on. \textit{Garbage} refers technically to wet discards--- food remains, yard waste, and offal. Refuse is an inclusive term for both the wet discards and the dry. Rubbish is even more inclusive: It refers to all refuse plus construction and demolition debris. The distinction between wet and dry garbage was important in the days when cities slopped garbage to pigs, and needed to have the wet material separated from the dry; it eventually became irrelevant, but may see a revival if the idea of composting food and yard waste catches on. We will frequently use "garbage" in this book to refer to the totality of human discards because it is the word used naturally in ordinary speech. The word is etymologically obscure, though it probably derives from Anglo-French, and its earliest associations have to do with working in the kitchen. \citep[9]{rathje1992rubbish}
\end{quote}
\end{singlespace}

@@

>>>>

%
% FROM Trash as Treasure BY WILLIAM L. FASH AND E. WYLLYS ANDREWS, ReVista
%\summary{Facts}
\begin{quote}
The World Bank estimates that the amount of solid waste generated in cities is growing faster than the rate of urbanization. The higher the income level and the rate of urbanization, the greater the amount of solid waste produced. OECD\footnote{OECD (Organization for Economic Co-operation and Development) is an international economic organization of 34 countries. Turkey is a member of this organization.} countries produce almost half of the world’s waste. Africa and South Asia produce the least waste. High-income countries have the highest collection rates and are most likely to dispose of waste to landfills or incinerators. Low-income countries have the lowest collection rates and are most likely to dispose of their waste in open dumps. However, low-income countries also have the largest numbers of informal waste pickers who collect, sort, and reclaim recyclables---thus reducing costs to the city and to the environment \citep{fash2015trash}.
\end{quote}

@@

%
%
%\summary{Parts of us}
\begin{quote}
Our trash is a testament; what we throw away says much about our values, our habits, and our lives. ... Our trash is part of us, whether or not we choose to acknowledge it. ... The absence of a waste stream aroused suspicion, just as the presence of particular items tell us about the habits of the consumers who generate a waste stream. \citep{zimring2012encyclopedia}
\end{quote}

@@

%
%
%\summary{Different disciplines of trash, narrowing down scope}
Trash attract the attention of different peoples and disciplines \quotes{ranging from economics to environmental studies, but most particularly by those studying consumerism or material culture} \citep{emgin2012trashion}. Technological perspectives are one of them. Trash is seen as a design and technological problem \citep{mcdonough2010cradle}.  
% Developed technologies and societies generates lots of trash, so this situation cause to inquiry that are they really developed? Developed in what sense? What are the criterion (foundation, measure) of technology? Technology is interested in which problems?)

@@

% FROM Recycled, Re-Seen: Folk Art from the Global Scrap Heap
In addition to these
\begin{quote}
%\vspace{-\baselineskip}
the process of [transformation] is not to be confused with the kind of industrial recycling to which we in the West are most accustomed. When we think of recycling in industrialized nations we imagine an automated sequence beginning with the curbside disposal of aluminum cans, plastic bottles, and old newspapers with the aim of returning them to the industrial process \citep{cerny1996recycled}. 
%\vspace{-\baselineskip}
\end{quote}

@@

% FROM Rubbish! The Archaeology of Garbage, p.9, rathje1992rubbish
\begin{quote}
Several words for the things we throw away---"garbage", "trash", "refuse", "rubbish"--- are used synonymously in causal speech but in fact have different meanings. \textit{Trash} refers specifically to discards that are at least theoretically "dry"---newspapers, boxes, cans, and so on. \textit{Garbage} refers technically to wet discards--- food remains, yard waste, and offal. Refuse is an inclusive term for both the wet discards and the dry. Rubbish is even more inclusive: It refers to all refuse plus construction and demolition debris. The distinction between wet and dry garbage was important in the days when cities slopped garbage to pigs, and needed to have the wet material separated from the dry; it eventually became irrelevant, but may see a revival if the idea of composting food and yard waste catches on. We will frequently use "garbage" in this book to refer to the totality of human discards because it is the word used naturally in ordinary speech. The word is etymologically obscure, though it probably derives from Anglo-French, and its earliest associations have to do with working in the kitchen. \citep[9]{rathje1992rubbish}
\end{quote}

@@

% FROM Susan Strasser
% According to the Oxford English Dictionary, recycling originated in the oil industry during the 1920s, describing partially refined petroleum sent through the refining cycle again to reduce waste. Its use broadened during the 1960s, designating all kinds of reuse and reclamation, and the world became familiar during the early 1970s, as the burgeoning environmental movement promoted the separate collection of certain kinds of trash to promote their reuse in manufacturing.

% RUBBISH NEWSPAPER

% All these variety of words forms her research and rubbish newspaper.

% these all words commonly used to refer is a subject of Alice Bradshaw's thesis and work. She analyzes each word in her rubbish newspaper. Figure X shows newspaper cover photo.

% The Museum of Contemporary Rubbish continues a tradition of celebrating and reversing the status of low culture objects within the ‘high status’ gallery space. Bradshaw reflects on this connection between rubbish and contemporary artistic practice in the Rubbish newspaper which is given away to visitors at the show. A large body of research is disseminated and contextualised in this throwaway (often unwanted) medium of the free newspaper. The subject of rubbish is broken down into its taxonomic elements (eg detritus, rejects, litter), these sub-categories become collections in themselves, of theories and works that have now been transformed through the disposable nature of the newspaper as medium. The paper communicates this research in a way which reflects on the content: through quotations, references and Bradshaw’s charmingly simplistic renderings of the artworks she cites, each section is made up of remains. Here, Bradshaw has linked a review of discarded waste with contemporary practice, and, even further, she adapts Walter Benjamin’s method in the paper made up of quotations, and an exhibition consisting of elements found whilst wandering the urban space. Connecting the writer’s earlier comparison of the poet and rag picker, here the artist becomes the collector and hoarder of waste.

% Her works shows us that the increasing interests on the subject starting from the beginning of the 20th century.

% use it "brings to mind"
